Recovering from population extinction in the Animal Life Cycle Algorithm (ALCA)

### 2022-09-23 paper.tex
Updated Experiments
Graphics improvement.

\usepackage{booktabs}       %Booktabs Table Style

@@

\begin{figure}
    \includegraphics[width=\textwidth]{img/fig_fun_ackley.pdf}
    \caption{Box and whisker chart for the Ackley Benchmark Function, 5 vs 10 Dimensions.} \label{fig.fun_ackley}
    \end{figure}

@@

\begin{figure}
    \includegraphics[width=\textwidth]{img/fig_fun_bohachevsky.pdf}
    \caption{Box and whisker chart for the Bohachevsky Benchmark Function, 5 vs 10 Dimensions.} \label{fig.fun_bohachevsky}
    \end{figure}

@@

\begin{figure}
    \includegraphics[width=\textwidth]{img/fig_fun_griewank.pdf}
    \caption{Box and whisker chart for the Griewank Benchmark Function, 5 vs 10 Dimensions.} \label{fig.fun_griewank}
    \end{figure}

@@

\begin{figure}
    \includegraphics[width=\textwidth]{img/fig_fun_rastrigin.pdf}
    \caption{Box and whisker chart for the Rastrigin Benchmark Function, 5 vs 10 Dimensions.} \label{fig.fun_rastrigin}
    \end{figure}

@@

\begin{figure}
    \includegraphics[width=\textwidth]{img/fig_fun_sphere.pdf}
    \caption{Box and whisker chart for the Sphere Benchmark Function, 5 vs 10 Dimensions.} \label{fig.fun_sphere}
    \end{figure}

>>>>

\usepackage{booktabs}       % Booktabs Table Style

\usepackage{graphicx}       % To frame graphic images
\usepackage[export]{adjustbox}

@@

The goal of our fist experiment was to have fun, while improving the graphics with best images.

\begin{figure}
    \includegraphics[width=\linewidth, frame]{img/fig_fun_ackley.pdf}
    \caption{Box and whisker chart for the Ackley Benchmark Function, 5 vs 10 Dimensions.} \label{fig.fun_ackley}
    \end{figure}

@@

\begin{figure}
    \includegraphics[width=\linewidth, frame]{img/fig_fun_bohachevsky.pdf}
    \caption{Box and whisker chart for the Bohachevsky Benchmark Function, 5 vs 10 Dimensions.} \label{fig.fun_bohachevsky}
    \end{figure}

@@

\begin{figure}
    \includegraphics[width=\linewidth, frame]{img/fig_fun_griewank.pdf}
    \caption{Box and whisker chart for the Griewank Benchmark Function, 5 vs 10 Dimensions.} \label{fig.fun_griewank}
    \end{figure}

@@

\begin{figure}
    \includegraphics[width=\linewidth, frame]{img/fig_fun_rastrigin.pdf}
    \caption{Box and whisker chart for the Rastrigin Benchmark Function, 5 vs 10 Dimensions.} \label{fig.fun_rastrigin}
    \end{figure}

@@

\begin{figure}
    \includegraphics[width=\linewidth, frame]{img/fig_fun_sphere.pdf}
    \caption{Box and whisker chart for the Sphere Benchmark Function, 5 vs 10 Dimensions.} \label{fig.fun_sphere}
    \end{figure}
